### 2010-10-25 trunk/papers/webist2011/paper_sec_wrapping.tex
changes made by Albert
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1024 d8b0c59b-6544-0410-94d9-83a5658a058e
added some changes changes
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1034 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{listing}
\begin{verbatim}
http://open.api.sandbox.ebay.com/shopping?appid=KasselUn-efea-4b93-9505-5dc2ef1ceecd
  &version=517&callname=FindItems&ItemSort=EndTime&QueryKeywords=USB&responseencoding=XML
\end{verbatim}
\end{listing}

@@

Our tool follows an interactive paradigm. Therefore, any time a change to a transformation rule is done, the transformation process is triggered and the resulting facts tree is directly shown. This process helps the user to deal with the slightly complex semantics of the transformation rules avoiding errors or mistakes. In addition, our tool is ontology-driven, therefore the service wrapper designer retrieves the domain-specific types from a backend server (such as the catalogue discussed in Sect.~\ref{sec:discovery}) together with the structure of each type, i.e. together with a description of the attributes of each object. Thus, the transformation rule editor is able to provide selection boxes for the target element of the rules. For a \emph{createObject} rule, this selection box shows the object types available for that domain. For the \emph{fillAttributes} rules, the selection box shows the attributes of the object type chosen in the parent rule. In addition, we may provide some analysis tool, which will help to guarantee that the objects generated by the transformation rules conform to the object types defined in the corresponding conceptual model (see Sect.~\ref{ssec:ontology}). This helps to ensure that the objects generated by the designed service wrapper will be compatible for input parameters of subsequent filter steps and or gadgets.

>>>>

\begin{listing}
\begin{verbatim}
http://open.api.sandbox.ebay.com/shopping?
  appid=KasselUn-efea-4b93-9505-5dc2ef1ceecd&
  version=517&callname=FindItems&
  ItemSort=EndTime&QueryKeywords=USB&
  responseencoding=XML
\end{verbatim}
\end{listing}

@@

Our tool follows an interactive paradigm. Therefore, any time a change to a transformation rule is done, the transformation process is triggered and the resulting facts tree is directly shown. This process helps the user to deal with the slightly complex semantics of the transformation rules avoiding errors or mistakes. In addition, our tool is ontology-driven, therefore the service wrapper designer retrieves the domain-specific types from a backend server (such as the catalogue discussed in Section~\ref{sec:discovery}) together with the structure of each type, i.e. together with a description of the attributes of each object. Thus, the transformation rule editor is able to provide selection boxes for the target element of the rules. For a \emph{createObject} rule, this selection box shows the object types available for that domain. For the \emph{fillAttributes} rules, the selection box shows the attributes of the object type chosen in the parent rule. In addition, we may provide some analysis tool, which will help to guarantee that the objects generated by the transformation rules conform to the object types defined in the corresponding conceptual model (see Section~\ref{ssec:ontology}). This helps to ensure that the objects generated by the designed service wrapper will be compatible for input parameters of subsequent filter steps and or gadgets.
